Designing for Multiple Use and At-Risk Users: Tor Configuration Launcher

### 2016-03-29 pets2017-paper/pets2017-paper.tex
add in participant quotes

\subsubsection{Results} 
%\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
%    \item {\bfseries Task Completion} Almost all can successfully connect to Tor
%    \item {\bfseries Time to Completion} Time to complete, ease of user for the average user. 
%    \item {\bfseries Safe for High-Risk Users} It should be possible to configure Tor with the interface that it doesn't leak %that they are using Tor. 
%\end{enumerate}

{\color {red}
We noticed four common challenges:

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Challenge 1:} Users don't know how to choose between connecting directly to the Tor network or manually configuring their connection (Figure \ref{fig:window1}). The text was unread or not understood by most users. When the user read the text, they found no instructions, but were given information to make a decision for themselves, which they did not feel equipped to do.  
\item {\bfseries Challenge 2:} Users feel compelled to set up a bridge, even if they don't need one. We believe this is due to the text on the first screen, which refers to a ``censored internee connection'' (Figure \ref{fig:window1}). Bridges are only necessary when the government actively censored Tor relays, but participants are not able to determine the difference between a censor that blocks websites and a censor that blocks websites and the Tor network. 
\item {\bfseries Challenge 3:} Users did not know what to do after a failure. Error messages (see Figure \ref{fig:error}) did not guide users into taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
\item {\bfseries Challenge 4:} Users draw incorrect conclusions after a failed connection. The interface passively re-displayed the last window seen before the attempted connection (Figure \ref{fig:window4} or \ref{fig:window5}), regardless of the error.
\end{itemize}
}

>>>>

%\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
%    \item {\bfseries Task Completion} Almost all can successfully connect to Tor
%    \item {\bfseries Time to Completion} Time to complete, ease of user for the average user. 
%    \item {\bfseries Safe for High-Risk Users} It should be possible to configure Tor with the interface that it doesn't leak %that they are using Tor. 
%\end{enumerate}

We noticed four common challenges:

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Challenge 1:} Users don't know how to choose between connecting directly to the Tor network or manually configuring their connection (Figure \ref{fig:window1}). The text was unread or not understood by most users. When the user read the text, they found no instructions, but were given information to make a decision for themselves, which they did not feel equipped to do.  
\item {\bfseries Challenge 2:} Users feel compelled to set up a bridge, even if they don't need one. We believe this is due to the text on the first screen, which refers to a ``censored internee connection'' (Figure \ref{fig:window1}). Bridges are only necessary when the government actively censored Tor relays, but participants are not able to determine the difference between a censor that blocks websites and a censor that blocks websites and the Tor network. 
\item {\bfseries Challenge 3:} Users did not know what to do after a failure. Error messages (see Figure \ref{fig:error}) did not guide users into taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
\item {\bfseries Challenge 4:} Users draw incorrect conclusions after a failed connection. The interface passively re-displayed the last window seen before the attempted connection (Figure \ref{fig:window4} or \ref{fig:window5}), regardless of the error.
\end{itemize}

Relevant participant quotes: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item{{\bfseries P1}:``figuring out if the progress bar wasn't moving because the connection was censored, of if it was just slow''}
\item{{\bfseries P2}: "I don't know what any of those means (list of bridges), I don't know what that (proxy) means at all."}
\item{{\bfseries P3}: ``The vocabulary is really challenging, for someone not doing IT work. Good thing I'm really curious. because I was able to use trial and error.''} 
\item{{\bfseries P4}: ``When I saw obfs3 as the recommended option, the next option logically for me was obfs4.'}
\item{{\bfseries P5}: ``I tried the pluggable transport that used google, because I noticed that google was working (when I was using a non-Tor browser).''}
\item{{\bfseries P6}: ``The progress bar had no feedback for me. I didn't know why I was getting back `establishing encrypted directory'--what does that mean for me?''}
\item{{\bfseries P6}: ``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}
\item{{\bfseries P7}: ``The bridge screen was the most challenging. It seemed very technical to me. I don't know what a bridge is. Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen. I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).''}
\item{{\bfseries P8}: ``I have no clue what's the difference between flashrpoxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?''}
\item{{\bfseries P9}: ``Configure seemed manual, so I clicked connect.''} %c1
\item{{\bfseries P10}: ``I was censored, so I picked the configure.''} %c1
\item{{\bfseries P11}: ``Is this question (does your ISP censor your Internet connection) really necessary? I just selected that I have a censored connection, why do they ask me again?''}
\item{{\bfseries P11}: ``I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance.''}
\item{{\bfseries P12}: ``I decided which options to choose by process of elimination with trial and error.'' }
\item{{\bfseries P13}: ``I don't remember what I did. I figured it out? What? <laughs> Oh man, that's crazy.''}
\item{{\bfseries P14}: ``The words were confusing. I don't really understand computers. I don't know what configure means in this setting. Hmm, is it going to crash? When you see connect, you want to click it because you really want it to connect.''}
\item{{\bfseries P15}: ``Give this to a couple of people who know how to do this. They can feel elite... they only want the elite to use some computer things.''}
\item{{\bfseries P15}: ``I didn't know if this computer had any proxy information. I wasn't able to find it if it did.''}
\item{{\bfseries P16}: ``Because I never configured a proxy or worked with that stuff, I was just going to keep clicking and pray.''}
\item{{\bfseries P16}: ``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}
\end{itemize}
